---
title: "Assessment 1.3"
author: "Avinash Meka (s4648886)"
date: "29/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Data viz and wrangling


#Reading the libraries tidyverse, skimr and scales
```{r}
library(tidyverse)
library(skimr)
library(scales)
```


#Reading the dataset fastfood
```{r}
fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```


#identifying  the different types of variables using skimr packages.In the recorded data every variable has a pre-defined data type, along with the specific range mentioned with min and max(=variability).
#Salads,x column can be removed from the data set as they are unused.
```{r}
summary(fastfood)
fastfood%>%skim()
```


#changing the data types of restaurant with as_factor()and defining a class to display the changed data types to factors.
```{r}
fastfood$restaurant<-as_factor(fastfood$restaurant)
class(fastfood$restaurant)
```


#replacing NA with 0 in the dataset fastfood.
```{r}
fastfood[is.na(fastfood)] <- 0
```


#cut_number makes n groups with the number of observations. 
#Creating a new variable caloies_type and saving it to the dataset and using cut_number function assigning labels and making them ordered results.
```{r}
fastfood<-fastfood%>%
  mutate(calories_type=cut_number(calories,3,
                                  labels=c("low","medium","high"),ordered_results=TRUE))
```


#Data viz for calories_type in food items for each type of restaurant. Using facets and theme.
```{r}
fastfood%>%
  ggplot(aes(calories_type))+
  geom_bar()+
  facet_wrap(~restaurant)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


#Creating another new variable trans_fat_percentage to calculate the percentage of trans_fat and total_fat.
```{r}
fastfood<-fastfood%>%mutate(trans_fat_percent = trans_fat/total_fat)
```


#Data viz for trans_fat` in food items for each type of restaurant. Using facets and themes.
```{r}
fastfood%>%
  ggplot(aes(trans_fat))+
  geom_dotplot()+
facet_wrap(~ restaurant)  +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


#the average (mean) total_fat for each type of restaurant.
```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(mean(calories))%>%
  ungroup()
```


#dataviz that allow to compare different restaurants and mean(total_fat)
```{r}
fastfood%>%
  ggplot(aes(mean(calories) ))+
  geom_bar()
```