---
title: "Assessment 1.2"
author: "Avinash Meka (s4648886)"
date: "22/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Data wrangling

#loading packages `tidyverse and skimr`.
```{r}
library(tidyverse)
library(skimr)
```

#importing csv file into variable `fastfood`and displaying variable types using `skim`.
```{r}
fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

fastfood%>%skim()
```

#number of observations for each restaurant.
```{r}
fastfood%>%count(restaurant)
```

#calculating average number of calories for each restaurant.
```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(average_calories=mean(calories))%>%
  ungroup()
```

#adding `average_calories` to dataset.
```{r}
fastfood%>%
  group_by(restaurant)%>%
  mutate(average_calories=mean(calories))%>%
  ungroup()
```

#displaying `total_fat` using `geom_point`.
#The `geom_point` is used to create scatterplots. The scatterplots is most useful for displaying the relationship between two variables. As we are ploting total fat of different restaurants geom_point provides better data visualisation.

```{r}
fastfood%>%
  ggplot(aes(restaurant,total_fat))+
  geom_point()
```

#displaying count of observations per each type of restaurant.
```{r}
fastfood%>%
  count(restaurant)
```

#adding variable `max_total_fat` to dataset.
```{r}
fastfood%>%
  group_by(restaurant)%>%
  mutate(max_total_fat=max(total_fat))%>%
  ungroup()
```

#using `geom_point` for Mcdonalds to plot sugar variable against protein.
```{r}
fastfood%>%
  filter(restaurant=="Mcdonalds")%>%
  ggplot(aes(sugar,protein))+
  geom_point()
```

